Visualizations for article

### 2016-05-27 101-visualizations-for-article.Rmd
Push heatmap of NY1850

>>>>

```{r NY-most-borrowed, fig.height=8}
all_NY1850 <- data_frame(borrower_code = "NY1850",
                         borrower_section = all_matches %>% 
                           filter(borrower_code == "NY1850") %>% 
                           `$`("borrower_section") %>%
                           unique() %>%
                           sort()
                        )

NY1850_match_counts <- all_matches %>% 
  filter(match_code == "NY1850",
         borrower_year > 1850,
         score >= 0.1) %>% 
  count(match_section)

left_join(all_NY1850, NY1850_match_counts, 
          by = c("borrower_section" = "match_section")) %>% 
  select(section = borrower_section, n) %>% 
  mutate(n = ifelse(n < 6, NA, n)) %>% 
  mutate(n = cut(n, c(seq(0, 40, 5), 85))) %>% 
  mutate(.,
         column = col_vector(nrow(.), 50),
         row = row_vector(nrow(.), 50)) %>% 
  ggplot(aes(x = column, y = -row, fill = n)) +
  geom_tile(color = "lightgray") +
  scale_fill_brewer(palette = "YlOrBr", na.value = "white", 
                    labels = c("6-10", "11-15", "16-20", "21-25", "26-30",
                               "31-35", "36-40", "40+")) +
  labs(x = NULL, y = NULL, fill = "Number of time borrowed") + 
  coord_equal() + 
  theme_minimal() + 
  theme(legend.position = "bottom",
      axis.ticks = element_blank(),
      axis.line = element_blank(), axis.text = element_blank(),
      panel.background = element_blank(), panel.grid = element_blank(),
      legend.key.size = unit(0.5, "cm"),
      plot.margin = unit(c(0, 0, 0, 0), "cm"),
      plot.title = element_text(hjust = 0.5)) +
  ggtitle("Most frequently borrowed sections in NY1850")

```
